Nock for Everyday Coders

### 2025-01-24 mss.tex
Post

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              Manuscript submitted for review.\\
              % {\it Urbit Systems Technical Journal} II:1 (2024):  1–3. \\
              ~ \\
              Address author correspondence to \authorpatp.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{Nock for Everyday Coders}
\fancyfoot[LE,RO]{\thepage}

@@

How do you say which slot number you want from the tree?  We say that:

@@

\noindent{}
This permits the address to be defined within a particular subtree as well as within the overall tree.

>>>>

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              % Manuscript submitted for review.\\
              {\it Urbit Systems Technical Journal} II:1 (2025):  1–46. \\
              ~ \\
              Address author correspondence to \authorpatp.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{Nock for Everyday Coders}
\fancyfoot[LE,RO]{\thepage}

@@

\noindent{}
This permits the address to be defined within a particular subtree as well as within the overall tree (Figure \ref{fig:treefull}).

\begin{figure}[hbt!]
  \centering
  \caption{A binary tree with labeled node addresses to several layers. \label{fig:treefull}}
  {
    \begin{tikzpicture}
    [->,>=stealth',level 1/.style={sibling distance = 8cm/#1, level distance = 1.5cm},level 2/.style={sibling distance = 4cm/#1, level distance = 1.5cm},level 3/.style={sibling distance = 2cm/#1, level distance = 1.5cm},level 4/.style={sibling distance = 1cm/#1, level distance = 1.5cm},scale=0.6, transform shape]
    \node [subtree] {\Large 1}
    child {
      node [subtree] {\Large 2} 
      child {
        node [subtree] {\Large 4} 
        child {
          node [subtree] {\Large 8} 
          child {
            node [treenode] {\Large 16} 
            }
          child {
            node [treenode] {\Large 17} 
          }
          }
        child {
          node [subtree] {\Large 9} 
          child {
            node [treenode] {\Large 18} 
          }
          child {
            node [treenode] {\Large 19} 
          }
          }
          }
      child {
        node [subtree] {\Large 5} 
        child {
          node [subtree] {\Large 10} 
          child {
            node [treenode] {\Large 20} 
          }
          child {
            node [treenode] {\Large 21} 
          }
        }
        child {
          node [subtree] {\Large 11} 
          child {
            node [treenode] {\Large 22} 
          }
          child {
            node [treenode] {\Large 23} 
          }
        }
          }
    }
    child {
      node [subtree] {\Large 3} 
      child {
        node [subtree] {\Large 6} 
        child {
          node [subtree] {\Large 12} 
          child {
            node [treenode] {\Large 24} 
          }
          child {
            node [treenode] {\Large 25} 
          }
        }
        child {
          node [subtree] {\Large 13} 
          child {
            node [treenode] {\Large 26} 
          }
          child {
            node [treenode] {\Large 26} 
          }
        }
    }
      child {
        node [subtree] {\Large 7} 
        child {
          node [subtree] {\Large 14} 
          child {
            node [treenode] {\Large 28} 
          }
          child {
            node [treenode] {\Large 29} 
          }
        }
        child {
          node [subtree] {\Large 15} 
          child {
            node [treenode] {\Large 30} 
          }
          child {
            node [treenode] {\Large 31} 
          }
        }
      }
    }
    ;
    \end{tikzpicture}
  }
\end{figure}

That is, how do you say which slot number you want from a given tree?  We say that:

@@
